Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/hybrid_zone.tex
pulled together the arguments about cline generality

We model selection through a single, underdominant locus:
at this locus, there are two alleles, one corresponding to each of the ancestral populations.
Individuals who are heterozygous at this locus produce on average $1-s$ times as many offspring than either homozygote.
Although most selection in hybrid zones is likely more complex than this simple situation, 
previous work has shown that such models generate clines that are very similar to models of ecological selection or epistatic systems \citep{Kruuk1999,barton2000epistasis}, 
\yb{because selection on an allele depends on its marginal effect on fitness.  
Exceptionally strong epistatic selection which acts more quickly than free recombination may therefore, yield results that differ slightly from ours. 
Likewise, while we do not model ecological selection, previous theory shows that clines formed by under dominant selection and extransic selection are essential indistinguishable, especially over short time scales when there is little time for clines to wobble \citep{Barton1979a}}.
\plr{(Merge paragraph from into into here?)}

>>>>

We model selection through a single, underdominant locus:
at this locus, there are two alleles, one corresponding to each of the ancestral populations.
Individuals who are heterozygous at this locus produce on average $1-s$ times as many offspring than either homozygote.
Although most selection in hybrid zones is likely more complex than this simple situation, 
previous work has shown that such models generate clines that are very similar to models of ecological selection or epistatic systems \citep{Kruuk1999,barton2000epistasis}, 
\yb{because selection on an allele depends on its marginal effect on fitness.  }
Exceptionally strong epistatic selection which acts more quickly than free recombination may therefore, yield results that differ slightly from ours. 
Likewise, while we do not model ecological selection, theoretical and simulation studies show that clines formed by underdominant selection and extrinsic selection are effectively indistinguishable without additional information \citep{may1975gene,Barton1993,Kruuk1999}, especially over short time scales \citep{Barton1979a}, \linelabel{ll:all_clines_are_the_same}
with their shape determined mostly by the mean fitness of the heterozygote \citep{Slatkin1973}.
